---
title: "Join Event Catch Examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Guide to join_event_catch}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(EMAdownload)
```

This vignette will walk through several possible use cases for the join_event_catch() function and provide examples 

### Pull all Juvenile Chinook positive catches from all tows from all years from Northern Bering Sea

```{r}
df <- join_event_catch(start_year = 2002, # Defaults to 2002 if no argument entered.
                       end_year = 2024,
                       survey_region = "NBS",
                       tsn = 161980,
                       lhs = "J",
                       gear = c("CAN","Nor264","NETS156","MAR"),
                       trawl_method = c("S","M","O"),
                       catch0 = FALSE)

nrow(df); head(df)
```

### Pull all age-0 pollock from surface trawls in all survey regions

```{r}
df <- join_event_catch(start_year = 2002, # Defaults to 2002 if no argument entered.
                       end_year = 2024,
                       survey_region = c("SEBS","NBS","Chukchi"),
                       tsn = 934083,
                       lhs = "A0",
                       gear = c("CAN","Nor264"), # There are no NETS156 or MAR surface trawls.
                       trawl_method = c("S"),
                       catch0 = FALSE)

nrow(df); head(df)
```

### Pull all juvenile salmon catches from surface trawls in the Northern Bering Sea and include zero-catches

```{r}
df <- join_event_catch(start_year = 2002, # Defaults to 2002 if no argument entered.
                       end_year = 2024,
                       survey_region = c("NBS"),
                       tsn = c(161975,161976,161977,161979,161980),
                       lhs = "J",
                       gear = c("CAN"), # There are no Nor264 surface trawls in NBS.
                       trawl_method = c("S"),
                       catch0 = TRUE)

nrow(df); head(df)
```

### Pull all age-0 pacific cod from non-surface trawls in the Southeastern Bering Sea between 2008 and 2018 and include zero-catches

```{r}
df <- join_event_catch(start_year = 2008, # Defaults to 2002 if no argument entered.
                       end_year = 2018,
                       survey_region = "SEBS",
                       tsn = 164711,
                       lhs = "A0",
                       gear = c("CAN","NETS156","Nor264","MAR"), 
                       trawl_method = c("M","O"),
                       catch0 = TRUE)

nrow(df); head(df)
```
